library(ggplot2)
library(dplyr)
library(gridExtra)
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')

```{r}
pf.fc_by_age_gender <- subset(pf, !is.na(gender)) %>%
  group_by(age, gender) %>%
  summarise(mean_friend_count = mean(friend_count),
            median_friend_count = median(friend_count),
            n = n()) %>%
  ungroup() %>%
  arrange(age)

head(pf.fc_by_age_gender)
```

```{r}
ggplot(data = pf.fc_by_age_gender, aes(age, median_friend_count))+
  geom_line(aes(color = gender))
```
```{r}
library(tidyr)
pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
                                  age ~ gender,
                                  value.var = 'median_friend_count')

head(pf.fc_by_age_gender.wide)
```

```{r}
ggplot(data = pf.fc_by_age_gender.wide, aes(age, female/male))+
  geom_line(color = 'orange')+
  geom_hline(yintercept = 1, linetype = 2)
```

```{r}
pf$year_joined <-  2014 - ceiling(pf$tenure / 365)
summary(pf$year_joined)
table(pf$year_joined)
```

```{r}
pf$year_joined.bucket <- cut(pf$year_joined, breaks = c(2004, 2009, 2011, 2012, 2014))
summary(pf$year_joined.bucket)
```

```{r}
## Median friend count across age-group cohorts.
ggplot(data = subset(pf, !is.na(year_joined.bucket)), aes(age, friend_count))+
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)
```

```{r}
## Average friend count for age-group cohorts.

ggplot(data = subset(pf, !is.na(year_joined.bucket)), aes(age, friend_count))+
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean)+
  geom_line(aes(y = friend_count), linetype = 2, stat = 'summary', fun.y = mean)

```

```{r}
## Friending Rate
friend_rate <- pf %>%
  filter(tenure > 0)%>%
  #group_by(year_joined.bucket) %>%
  summarise(mean_friending_rate = mean(friend_count / tenure),
            median_friending_rate = median(friend_count /tenure),
            min_friending_rate = min(friend_count /tenure),
            max_friendin_rate = max(friend_count / tenure))

## Much easier way to accomplish the same as above

with(subset(pf, tenure > 0), summary(friend_count / tenure))

```

```{r}
# Line graph of mean of friendships_initiated per day (of tenure)
# vs. tenure colored by year_joined.bucket.

ggplot(data = subset(pf, tenure > 1), aes(tenure, friendships_initiated / tenure))+
  geom_smooth(aes(color = year_joined.bucket))
```

```{r}
yo <- read.csv('yogurt.csv')
yo$id <- factor(yo$id)
head(yo)
```
```{r}
qplot(data = yo, x = price)
```

